\chapter{Findings' validation interviews} \label{app:interview}

Hello my name is Marcello Steiner, a Chalmers' student conducting a study focused on technical debt and UI testing. I'd like to assure you that your answers will be completely anonymized and I will be the only one having access to the raw data.

Finally, if any of the following is not clear please ask me for further explanation.


\begin{enumerate}
    \item Can you briefly tell me on which projects you work or worked during the last year?
    
    \item What is your take about code duplication in terms of code maintainability?
    
    \item Can you pinpoint the cause of the code duplication that is already inside the code-base?
    
    \item When do you consider a function to be too complex? How do you refactor said function when facing one?
    
    \item As for question number 3, what is the the triggering cause of over-complex functions.
    
    \item How do you define a function scope?
    
    \item In your opinion, when is a statement too complex? How do you refactor a code-base filled with too complex-statements?
    
    \item What is the effect of too many complex statements in terms of maintainability?
    
    \item What is your opinion on high-arity functions? What about their maintainability?
    
    \item How do you decide when is best to use a determinate testing technology? What do you do when you see that some parts of the test suite use the wrong technology for the job?
    
    \item Does picking the wrong technology affect maintenance? If yes, how?
    
    \item Did you have any problem working with with the UFT objects' database? If yes, can you describe them to me and if there is a way to avoid them?
    
    
\end{enumerate}

Thank you for taking part in this study. Please avoid talking with your colleagues about what we discussed here. I'd like to repeat that this conversation will be stricly confidential.